Privacy-Preserving Localization Using Private Linear-Combination Aggregation

### 2021-05-21 main.tex
Draft for section on our linear-combination aggregator oblivious scheme finished Proof has been moved to appendix and both appendix section draft finished as well

\subsection{Estimation problem} \label{subsec:est_problem}
The estimation problem we consider, for which we will reduce communication to the protocol required for the introduced cryptographic problem, is localisation with range-only sensors. In this work, we will focus on the two-dimensional case for simplicity but will derive methods suitable for extension to a three-dimensional equivalent. The state that we wish to estimate captures the navigator position and the change in position ($\Delta$), and is given by
\begin{equation}
    \vec{x} = 
    \begin{bmatrix}
        x & \Delta x & y & \Delta y
    \end{bmatrix}^\top\,. \label{eqn:state_definition}
\end{equation}
The state evolves following a known system model, which at timestep $k$ is given by
\begin{equation}
    \vec{x}_k = \vec{f}(\vec{x}_{k-1})+\vec{w}_k\,, \label{eqn:system_model}
\end{equation}
with system noise covariance $\mathsf{Cov}[\vec{w}_k]=\mat{Q}_k$. The measurement model is dependent on sensor $i$'s location,
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        s_{x,i} & s_{y,i}
    \end{bmatrix}^\top\,,
\end{equation} 
and is given by
\begin{equation}
    z_{k,i} = h_i(\vec{x}_k)+v_{k,i}\,, \label{eqn:measurement_model}
\end{equation}
with measurement noise variance $\mathsf{Var}[v_{k,i}] = r_i$ and measurement function $h_i$, for sensor $i$, as
\begin{equation}
    \begin{split}
        h_i(\vec{x}) &= \left\lVert
        \begin{bmatrix}
            x & y
        \end{bmatrix}^\top
        - \vec{s}_{i}\right\rVert \\
        &= \sqrt{(x-s_{x,i})^2 + (y-s_{y,i})^2}\,.
    \end{split}
\end{equation}

@@

When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, summation and decryption are computed by the functions
\begin{equation}
    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2} \label{eqn:agg_summation}
\end{equation}
and
\begin{equation}
    \sum^{n}_{i=1}a^{(t)}_{i} = \frac{c^{(t)}-1}{N}\,. \label{eqn:agg_decryption}
\end{equation}
Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
\begin{equation*}
    \begin{split}
        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{a_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{a_{i,t}} \pmod{N^2} \\
        \equiv &(N+1)^{\sum^n_{i=1}a_{i,t}} \pmod{N^2}\,,
    \end{split}
\end{equation*}
removing all noise terms.

@@

We will consider a subset of rational numbers in terms of a range $M \in \mathbb{N}$ and fractional precision $\phi \in \mathbb{N}$. This contrasts with the common definition in terms of total and fractional bits \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not a power of two. A rational subset $\mathbb{Q}_{M,\phi}$ is then given by
\begin{equation}
    \mathbb{Q}_{M,\phi} = \left\{q \,\middle|\, \phi q \in \mathbb{N} \wedge -\left\lfloor\frac{M}{2}\right\rfloor \leq \phi q < \left\lfloor\frac{M}{2}\right\rfloor \right\}\,,
\end{equation}
and we can quantize any real number $a$ by taking the nearest rational $q \in \mathbb{Q}_{M,\phi}$, that is, $\argmin_{q\in\mathbb{Q}_{M,\phi}} |a-q|$. In this form, mapping rationals $\mathbb{Q}_{M,\phi}$ to an encryption range $\mathbb{Z}_N$ is achieved by choosing $M=N$ and the handling negatives by modulo arithmetic. Additionally, we note that the Q number format requires a precision factor $\phi$ to be removed after each encoded multiplication. This is captured by a third parameter $d$; the number of multiplication factors to add or remove from encodings.

@@

% TODO up to here

This encoding scheme provides the following homomorphic operations,
\begin{equation}
    \begin{split}
        \mathsf{E}_{M,\phi,d}(a_1) + \mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
        &\mathsf{E}_{M,\phi,d}(a_1+a_2)
    \end{split}\label{eqn:encoding_homomorphic_add}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mathsf{E}_{M,\phi,d}(a_1)\mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
        &\mathsf{E}_{M,\phi,d+1}(a_1a_2)\,,
    \end{split}
\end{equation}
noting that when $M=N$, the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:paillier_hom_plain_add}, \eqref{eqn:paillier_hom_mult} and therefore \eqref{eqn:our_scheme_lin_comb}.

%should also reference the modulo sum in the J-L scheme (which is missing in Eq. 14!!)

The choice of a high fractional precision $\phi$ may reduce quantization errors introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications. Given the largest number of expected multiplications $d_{max}$, and the largest expected decoded value $a_{max}$, the parameter should be chosen such that the following condition holds
\begin{equation}
    \left|\phi^{d_{max}+1}a_{max}\right| < \left\lfloor \frac{M}{2} \right\rfloor\,.
\end{equation}
In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $M=N$.

@@

\section{Private Linear-Combination Aggregation Scheme} \label{sec:lcao_scheme}

% From the crypto problem statement section - better suited here somewhere as IND-CPA and AO have not been introduced there yet
From the informal definitions above, it is clear that weights encrypted by an IND-CPA secure encryption scheme are sufficient for the first requirement, while a scheme satisfying AO is not sufficient for the second. To formalize the second requirement, we define a novel encryption type ``Linear-Combination Aggregator Oblivious Encryption'' and an accompanying security game, which capture the additional weights and modified leakage of AO.

In the next section, we will give a solution to an encryption scheme meeting LCAO security, with IND-CPA secure weight encryption, and give a cryptographic proof for its security.

% OUR SCHEME MEETING LCAO SECURITY

\label{subsec:our_scheme}
Our scheme is based on the Paillier and Joye-Libert schemes introduced in Sections \ref{subsec:paillier_scheme} and \ref{subsec:joye_libert_scheme}, and similarly bases its security on the DCRA. As with Joye-Libert's private aggregation scheme, a trusted party is required for the initial distribution of user secret keys. Below, we give definitions for the four algorithms comprising the linear-combination aggregation encryption scheme.

\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose an $m>1$ as the number of weights to combine, and set public parameter $\mathsf{pub}=H$, aggregator public key $pk_0 = N$ and aggregator private key $sk_0=(p,q)$. The remaining user secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.

    \item[$\mathsf{Enc}(pk_0, x)$] Encryption of values is computed as a Paillier encryption with implicit generator $g=N+1$. This is given by
    \begin{equation}
        \mathcal{E}_{pk_0}(x) = (N+1)^{x}\rho^N \pmod{N^2}\,, \label{eqn:our_scheme_encrypt}
    \end{equation}
    for a randomly chosen $\rho \in \mathbb{Z}_N$.

    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] The linear combination encryption step at instance $t$ is computed as 
    \begin{equation}
        l^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} \pmod{N^2}\,,\label{eqn:our_scheme_lin_comb}
    \end{equation}
    and makes use of the homomorphic property \eqref{eqn:paillier_hom_mult}. Correctness follows from
    \begin{equation*}
        \begin{split}
             l^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(a^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{a^{(t)}_{i,j}\omega^{(t)}_j} \rho^{N}_{j} \pmod{N^2} \\
            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j} \rho_{i}^{N} \pmod{N^2}\,,
        \end{split}
    \end{equation*}
    for some values $\rho_i,\rho_j \in \mathbb{Z}_N\,,1\leq j \leq m$. Here, $\rho_i^N$ and $H(t)^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.

    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] Aggregation is computed as $l^{(t)} = \prod^n_{i=1}l^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and is followed by Paillier decryption
    \begin{equation}
        \begin{split}
            \sum^{n}_{i=1}\sum^{m}_{j=1}&a^{(t)}_{i,j}\omega^{(t)}_j =\\
            &\frac{L((l^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,,
        \end{split} \label{eqn:our_scheme_decrypt}
    \end{equation}
    with $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$. The correctness of aggregation can be seen from
    \begin{align*}
        l^{(t)} &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}a_{i,j}\omega_j}\rho_i^N \pmod{N^2} \\
        \begin{split}
            &= H(t)^{\sum^n_{i=1}sk_i}\cdot \\
            &\qquad\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho_i^N \pmod{N^2}
        \end{split}\\
        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho'^N \pmod{N^2}\,,
    \end{align*}
    for some values $\rho_i,\rho' \in \mathbb{Z}_N,\,1\leq i \leq n$.
\end{LaTeXdescription}

Additionally, we note that in the above construction, all weights $\omega^{(t)}_j$ and values $a^{(t)}_{i,j}$ are integers, and that resulting linear combinations and summations are computed $\pmod{N}$.

\begin{remark} \label{rem:lcao_implicit_weight}
    The construction of this scheme additionally supports the linear combination of the implicit weight, $\omega^{(t)}_j = 1$, by replacing
    \begin{equation}
        \mathcal{E}_{pk_0}(1)^{a^{(t)}_{i,j}} = (N+1)^{1}\rho_j^N \pmod{N^2}
    \end{equation}
    in \eqref{eqn:our_scheme_lin_comb} by
    \begin{equation}
        (N+1)^{a^{(t)}_{i,j}} \pmod{N^2}\,,
    \end{equation}
    due to the removal of $\rho_j^N$ terms during decryption. This can be used to reduce the broadcast communication cost by one weight.
\end{remark}

% PROOF

To prove the security of our introduced scheme, we recall the desired security properties of an LCAO secure scheme with IND-CPA secure encrypted weights. From the definition above, weights encrypted with public key $pk_0$ are identical to encryptions of the Paillier scheme and therefore meet security notion IND-CPA. We omit this proof here and refer readers to the security proof of the Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} instead.

To show our scheme meets the security notion of LCAO, we prove by contrapositive that for an adversary $\mathcal{A}$ playing against a challenger using \textit{our scheme}, we can create an adversary $\mathcal{A}'$ playing against a challenger $\mathcal{C}$ using the \textit{Joye-Libert scheme}, such that
\begin{equation*}
    \mathsf{Adv}^{LCAO}(\mathcal{A}) > \eta_1(\kappa) \implies \mathsf{Adv}^{AO}(\mathcal{A}') > \eta_2(\kappa)\,,
\end{equation*}
for some negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$. (\textit{i.e.}, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) Given the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, we know our scheme must be LCAO secure and will thus conclude our proof. The proof overview has been given in Figure \ref{fig:proof_summary}. Additionally, the function $H$ used by our scheme is treated as a \textit{random oracle} in the Joye-Libert AO proof and will, therefore, prove our scheme secure in the random oracle model as well.

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize,scale=0.95]
    % Bounding box
    \draw [gray] (0,0) rectangle (6.5,6.5);

    \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
    \draw [-latex] (4.5,2.5) -- (4.5,1.75);
\end{tikzpicture}
\caption{High-level overview of our scheme's LCAO security proof.}
\vspace{-\baselineskip}
\label{fig:proof_summary}
\end{figure}

@@

\appendices
\section{Linear-Combination Aggregator Oblivousness (LCAO)} \label{app:lcao}
\begin{LaTeXdescription}
    \item[Setup] The challenger chooses security parameter $\kappa$, runs the $\mathsf{Setup}(\kappa)$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
    \begin{LaTeXenumerate}
        \item \textit{Encryption:} The attacker chooses a value $x$ and computes an encryption of $x$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(x)$.
        \item \textit{Weight Queries:} The attacker chooses an instance $t$ and receives the weights for that instance encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ and $(i',t',a^{\prime(t')}_{i',1},\dots,a^{\prime(t')}_{i',m})$, the following condition holds:
        \begin{equation*}
            i = i' \wedge t = t' \implies a^{(t)}_{i,j} = a^{\prime(t')}_{i',j},\,1\leq j\leq m\,.
        \end{equation*}
        The attacker is then given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{LaTeXenumerate} 
    \item[Challenge] Next, the attacker chooses an instance $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for the instance $t^*$, and no compromise queries, are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \left\langle\left(i,t^*,a^{(t^*)(0)}_{i,1},\dots,a^{(t^*)(0)}_{i,m}\right)\,\middle|\,i \in S\right\rangle
    \end{equation*}
    and
    \begin{equation*}
        \left\langle\left(i,t^*,a^{(t^*)(1)}_{i,1},\dots,a^{(t^*)(1)}_{i,m}\right)\,\middle|\, i \in S\right\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.}, the aggregator is compromised) and $S = U$, it is additionally required that
    \begin{equation*}
        \sum_{i\in S}\sum^{m}_{j=1} a^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} a^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
    \end{equation*}
    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen instance $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \left\langle\mathcal{E}_{pk_0,sk_i}\left(\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i\in S\right\rangle\,.
    \end{equation*}
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game if and only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{LaTeXdescription}

>>>>

\subsection{Estimation problem} \label{subsec:est_problem}
The estimation problem we consider, for which we will reduce communication to the protocol required for the introduced cryptographic problem, is localisation with range-only sensors. In this work, we will focus on the two-dimensional case for simplicity but will derive methods suitable for extension to a three-dimensional equivalent. The state that we wish to estimate captures the navigator position and the change in position ($\Delta$), and is given by
\begin{equation}
    \vec{x} = 
    \begin{bmatrix}
        x & \Delta x & y & \Delta y
    \end{bmatrix}^\top\,. \label{eqn:state_definition}
\end{equation}
The state evolves following a known system model, which at timestep $k$ is given by
\begin{equation}
    \vec{x}_k = \vec{f}(\vec{x}_{k-1})+\vec{w}_k\,, \label{eqn:system_model}
\end{equation}
with system noise covariance $\mathsf{Cov}[\vec{w}_k]=\mat{Q}_k$. The measurement model is dependent on sensor $i$'s location,
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        s_{x,i} & s_{y,i}
    \end{bmatrix}^\top\,,
\end{equation} 
and is given by
\begin{equation}
    z_{k,i} = h_i(\vec{x}_k)+v_{k,i}\,, \label{eqn:measurement_model}
\end{equation}
with Gaussian measurement noise $v_{k,i} \sim \mathcal{N}(0,r_i)$ and measurement function $h_i$, for sensor $i$, as
\begin{equation}
    \begin{split}
        h_i(\vec{x}) &= \left\lVert
        \begin{bmatrix}
            x & y
        \end{bmatrix}^\top
        - \vec{s}_{i}\right\rVert \\
        &= \sqrt{(x-s_{x,i})^2 + (y-s_{y,i})^2}\,.
    \end{split}
\end{equation}

@@

When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, summation and decryption are computed by the functions
\begin{equation}
    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2} \label{eqn:agg_summation}
\end{equation}
and
\begin{equation}
    \sum^{n}_{i=1}a^{(t)}_{i} = \frac{c^{(t)}-1}{N} \pmod{N}\,. \label{eqn:agg_decryption}
\end{equation}
Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
\begin{equation*}
    \begin{split}
        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{a_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{a_{i,t}} \pmod{N^2} \\
        \equiv &(N+1)^{\sum^n_{i=1}a_{i,t}} \pmod{N^2}\,,
    \end{split}
\end{equation*}
removing all noise terms.

@@

We will consider a subset of rational numbers in terms of a range $M \in \mathbb{N}$ and fractional precision $\phi \in \mathbb{N}$. This contrasts with the common definition in terms of total and fractional bits \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not a power of two. A rational subset $\mathbb{Q}_{M,\phi}$ is then given by
\begin{equation}
    \mathbb{Q}_{M,\phi} = \left\{q \,\middle|\, \phi q \in \mathbb{N} \wedge -\left\lfloor\frac{M}{2}\right\rfloor \leq \phi q < \left\lfloor\frac{M}{2}\right\rfloor \right\}\,,
\end{equation}
and we can quantize any real number $a$ by taking the nearest rational $q \in \mathbb{Q}_{M,\phi}$, that is, $\argmin_{q\in\mathbb{Q}_{M,\phi}} |a-q|$. In this form, mapping rationals $\mathbb{Q}_{M,\phi}$ to an encryption range $\mathbb{Z}_N$ is achieved by choosing $M=N$ and handling negatives by modulo arithmetic. Additionally, we note that the Q number format requires a precision factor $\phi$ to be removed after each encoded multiplication. This is captured by a third parameter $d$; the number of multiplication factors to add or remove from encodings.

@@

This encoding scheme provides the following homomorphic operations,
\begin{equation}
    \begin{split}
        \mathsf{E}_{M,\phi,d}(a_1) + \mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
        &\mathsf{E}_{M,\phi,d}(a_1+a_2)
    \end{split}\label{eqn:encoding_homomorphic_add}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mathsf{E}_{M,\phi,d}(a_1)\mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
        &\mathsf{E}_{M,\phi,d+1}(a_1a_2)\,,
    \end{split}
\end{equation}
noting that when $M=N$, the modulus corresponds with those in the Paillier homomorphic operations \eqref{eqn:paillier_hom_plain_add}, \eqref{eqn:paillier_hom_mult} and the Joye-Libert sum \eqref{eqn:agg_decryption}.

In general, the choice of a large precision parameter $\phi$ may reduce quantization errors introduced in \eqref{eqn:encode}, but risks overflow after too many multiplications. Given the largest number of encoded multiplications, $d_{max}$, and the largest value to be encoded $a_{max}$, the parameter should be chosen such that
\begin{equation}
    \left|\phi^{d_{max}+1}a_{max}\right| < \left\lfloor \frac{M}{2} \right\rfloor\,.
\end{equation}
In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $M=N$.

@@

\section{Private Linear-Combination Aggregation Scheme} \label{sec:lcao_scheme}
In this section, we introduce an encryption scheme meeting the desired security properties in section \ref{subsec:crypto_problem}. The scheme is a combination of the Paillier and Joye-Libert schemes and provides encrypted weights meeting IND-CPA and encrypted aggregation meeting LCAO. Similarly to its constituents, the scheme bases its security on the DCRA and, as with the Joye-Libert scheme, requires a trusted party for initial key generation and distribution. The four algorithms defining our scheme are given as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose a the number of weights to combine $m>1$ and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$. Sensor secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.

    \item[$\mathsf{Enc}(pk_0, x)$] Public-key encryption is computed by the Paillier encryption scheme with implicit generator $g=N+1$. This is given by
    \begin{equation}
        \mathcal{E}_{pk_0}(x) = (N+1)^{x}\rho^N \pmod{N^2}\,, \label{eqn:our_scheme_encrypt}
    \end{equation}
    for a randomly chosen $\rho \in \mathbb{Z}_N$.

    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] Encrypted linear combination at instance $t$ is computed as 
    \begin{equation}
        l^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} \pmod{N^2}\,,\label{eqn:our_scheme_lin_comb}
    \end{equation}
    and makes use of the homomorphic property \eqref{eqn:paillier_hom_mult}. Correctness follows from
    \begin{equation*}
        \begin{split}
             l^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(a^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{a^{(t)}_{i,j}\omega^{(t)}_j} \rho^{N}_{j} \pmod{N^2} \\
            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j} \rho_{i}^{N} \pmod{N^2}\,,
        \end{split}
    \end{equation*}
    for some values $\rho_i,\rho_j \in \mathbb{Z}_N\,,1\leq j \leq m$. Here, $\rho_i^N$ and $H(t)^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.

    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] Aggregation is computed as $l^{(t)} = \prod^n_{i=1}l^{(t)}_i \pmod{N^2}$, removing the aggregation noise terms, and is followed by Paillier scheme decryption
    \begin{equation}
        \begin{split}
            \sum^{n}_{i=1}\sum^{m}_{j=1}&a^{(t)}_{i,j}\omega^{(t)}_j =\\
            &\frac{L((l^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,,
        \end{split} \label{eqn:our_scheme_decrypt}
    \end{equation}
    with $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$. The correctness of the aggregation can be seen from
    \begin{align*}
        l^{(t)} &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}a_{i,j}\omega_j}\rho_i^N \pmod{N^2} \\
        \begin{split}
            &= H(t)^{\sum^n_{i=1}sk_i}\cdot \\
            &\qquad\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho_i^N \pmod{N^2}
        \end{split}\\
        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho'^N \pmod{N^2}\,,
    \end{align*}
    for some values $\rho_i,\rho' \in \mathbb{Z}_N,\,1\leq i \leq n$.
\end{LaTeXdescription}
Additionally, we note that in the above construction, all weights $\omega^{(t)}_j$ and values $a^{(t)}_{i,j}$ are integers and the resulting linear combinations and aggregation are computed $\pmod{N}$.

The security proof of this scheme must show that both encrypted weights meet IND-CPA and encrypted aggregation meets LCAO. As weights are encrypted with the Paillier encryption scheme, the first requirement is already met. To show that aggregation meets LCAO, a reduction proof is given in appendix \ref{app:proof}.

Lastly, we make the following remark about a possible implicit weight.
\begin{remark} \label{rem:lcao_implicit_weight}
    The construction of the above scheme supports linearly combining the implicit weight $\omega^{(t)}_j = 1$, by replacing
    \begin{equation}
        \mathcal{E}_{pk_0}(1)^{a^{(t)}_{i,j}} = (N+1)^{1}\rho_j^N \pmod{N^2}
    \end{equation}
    in \eqref{eqn:our_scheme_lin_comb}, by
    \begin{equation}
        (N+1)^{a^{(t)}_{i,j}} \pmod{N^2}\,.
    \end{equation}
    This is due to the removal of $\rho_j^N$ terms during decryption and can be used to reduce the navigator's broadcast communication cost by a single weight when it is known that $\omega^{(t)}_j=1$.
\end{remark}

@@

\appendices
\section{Linear-Combination Aggregator Oblivousness (LCAO)} \label{app:lcao}
The following game between attacker and challenger defines the security notion of LCAO.
\begin{LaTeXdescription}
    \item[Setup] The challenger chooses security parameter $\kappa$, runs the $\mathsf{Setup}(\kappa)$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
    \begin{LaTeXenumerate}
        \item \textit{Encryption:} The attacker chooses a value $x$ and computes an encryption of $x$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(x)$.
        \item \textit{Weight Queries:} The attacker chooses an instance $t$ and receives the weights for that instance encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ and $(i',t',a^{\prime(t')}_{i',1},\dots,a^{\prime(t')}_{i',m})$, the following condition holds:
        \begin{equation*}
            i = i' \wedge t = t' \implies a^{(t)}_{i,j} = a^{\prime(t')}_{i',j},\,1\leq j\leq m\,.
        \end{equation*}
        The attacker is then given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{LaTeXenumerate} 
    \item[Challenge] Next, the attacker chooses an instance $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for the instance $t^*$, and no compromise queries, are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \left\langle\left(i,t^*,a^{(t^*)(0)}_{i,1},\dots,a^{(t^*)(0)}_{i,m}\right)\,\middle|\,i \in S\right\rangle
    \end{equation*}
    and
    \begin{equation*}
        \left\langle\left(i,t^*,a^{(t^*)(1)}_{i,1},\dots,a^{(t^*)(1)}_{i,m}\right)\,\middle|\, i \in S\right\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.}, the aggregator is compromised) and $S = U$, it is additionally required that
    \begin{equation*}
        \sum_{i\in S}\sum^{m}_{j=1} a^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} a^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
    \end{equation*}
    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen instance $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \left\langle\mathcal{E}_{pk_0,sk_i}\left(\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i\in S\right\rangle\,.
    \end{equation*}
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game if and only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{LaTeXdescription}
